### 2025-02-13 README.Rmd
update usage instructions

# Research compendium for Bartholdy et al. 2023

@@

- [R](https://cran.r-project.org/)
- [Quarto](https://quarto.org/)
- [Git](https://git-scm.com/downloads) (optional)

@@

`libx11-dev libicu-dev make zlib1g-dev libcurl4-openssl-dev libssl-dev libfontconfig1-dev libfreetype6-dev libfribidi-dev libharfbuzz-dev libjpeg-dev libpng-dev libtiff-dev pandoc libxml2-dev libgit2-dev`

@@

- Open the folder in your preferred IDE
- run `renv::restore()` to install the required R packages
- run `quarto::quarto_render("analysis/paper/paper.qmd", output_format = "pdf")` in the R console (requires installing **quarto** R package) or `quarto render analysis/paper/paper.qmd --to pdf` to produce a PDF
- find the pdf in `./analysis/paper/_output`

### Licenses

>>>>

# Research compendium for Bartholdy et al. 2024

@@

- [R](https://cran.r-project.org/)
- [Quarto](https://quarto.org/)
- [TeX](https://www.latex-project.org/get/)
- [Git](https://git-scm.com/downloads) (optional)

@@

`libx11-dev libicu-dev make zlib1g-dev libcurl4-openssl-dev libssl-dev libfontconfig1-dev libfreetype6-dev libfribidi-dev libharfbuzz-dev libjpeg-dev libpng-dev libtiff-dev pandoc libxml2-dev libgit2-dev gfortran`

@@

1. Open the folder in your preferred IDE
2. run `renv::restore()` to install the required R packages
3. run `quarto::quarto_render("analysis/paper/paper.qmd", output_format = "pdf")` in the R console (requires installing **quarto** R package) or `quarto render analysis/paper/paper.qmd --to pdf` to produce a PDF
4. find the pdf in `./analysis/paper/_output`

## Licenses
